Particular examples of planar integral point sets and their classification \footnote{ This work was carried out at Voronezh State University and supported by the Russian Science Foundation grant 19-11-00197. }

### 2025-11-17 AvdMomZvolA_examples/ips_examples.tex
[AMZA] Page geometry - still WIP
[AMZA] Keywords in Russian

@@

@@

\begin{equation}
	\mathcal{P}_8=
	\sqrt{1}/13*
	\{
	( 0 ; 0);
	( 8450 ; 0);
	( 12844 ; 0);
	( 21294 ; 0);
	( 29575 ; 0);
	%\\
	( -2366 ; -8112);
	( 10647 ; -14196);
	( 15022 ; -3696)
	\}
\end{equation}
%
\begin{figure}[h!]
\center{\includegraphics[width=0.6\linewidth]{./img/8_2535_1_other.png}}
\parbox{1\linewidth}{\caption{IPS of cardinality 8 and diameter 2535}
\label{8_2535_1_d680}}
\end{figure}

The set shown on Figure~\ref{8_2400_42_56f3} has an axis of symmetry, but it is $y$ axis, not $x$ axis.
Due to the fact that its characteristic is not 1,
the set cannot be rotated by $90^\circ$ but still be on lattice~\eqref{eq:char_lattice}:
$
	\mathcal{P}_{8y}=
	\sqrt{42}/1*\{( \pm1200 ; 0);
	( \pm529 ; 182);
	( \pm814 ; 152);
	( \pm440 ; 80)
	\}
$

>>>>

\sloppy \textheight = 230mm \textwidth = 155mm \topmargin = -3mm
\oddsidemargin=3mm \evensidemargin=4pt

@@

\paragraph{Ключевые слова.}
	целоудалённое множество,
	плоское целоудалённое множество,
	классификация плоских целоудалённых множеств,
	диаметр целоудалённого множества

@@

\begin{multline*}
	\mathcal{P}_8=
	\sqrt{1}/13*
	\{
	( 0 ; 0);
	( 8450 ; 0);
	( 12844 ; 0);
	( 21294 ; 0);
	( 29575 ; 0);
	\\
	( -2366 ; -8112);
	( 10647 ; -14196);
	( 15022 ; -3696)
	\}
\end{multline*}
%
\begin{figure}[h!]
\center{\includegraphics[width=0.6\linewidth]{./img/8_2535_1_other.png}}
\parbox{1\linewidth}{\caption{IPS of cardinality 8 and diameter 2535}
\label{8_2535_1_d680}}
\end{figure}

The set shown on Figure~\ref{8_2400_42_56f3} has an axis of symmetry, but it is $y$ axis, not $x$ axis.
Due to the fact that its characteristic is not 1,
the set cannot be rotated by $90^\circ$ but still be on lattice~\eqref{eq:char_lattice}:
\begin{equation*}
	\mathcal{P}_{8y}=
	\sqrt{42}/1*\{( \pm1200 ; 0);
	( \pm529 ; 182);
	( \pm814 ; 152);
	( \pm440 ; 80)
	\}
\end{equation*}
